---
title: "Question_1"
author: "Matt Kruger"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Reading in the data
```{r}
Baby_names <- readRDS("../data/PracData25/US_Baby_names/Baby_Names_By_US_State.rds")
music_charts <- readRDS("../data/PracData25/US_Baby_names/charts.rds")
HBO_credits <- readRDS("../data/PracData25/US_Baby_names/HBO_credits.rds")
HBO_titles <- readRDS("../data/PracData25/US_Baby_names/HBO_titles.rds")
```

Installing all necessary packages
```{r}
install.packages("pacman")
pacman::p_load("tidyverse")
pacman::p_load("lubdridate")
pacman::p_load("stringr")
pacman::p_load("ggridges")
pacman::p_load("patchwork")
pacman::p_load("stargazer")
pacman::p_load("gt")
pacman::p_load("webshot")
webshot::install_phantomjs()
pacman::p_load("webshot2")
```

Loading in functions
```{r}
list.files('code/', full.names = T, recursive = T) %>% .[grepl('.R', .)] %>% as.list() %>% walk(~source(.))
```

Wrangling the data so that a dataframe is created which only contains the correlation between the top 25 male and top 25 female names in the US in the current year and three years later, for each year 1900 - 2011. Note: The years 2012 - 2014 had to be dropped, as those years had no rankings in three years time to which they could be compared to.
```{r}
spearman_rank_df <- Baby_names %>% 
    group_by(Year, Name, Gender) %>% 
    summarise(Count = sum(Count)) %>%  #Aggregating the count per names per state, so that count represents the number of babies given that name in that year in the entirety of the US. The state column is dropped by this function.
    group_by(Year, Gender) %>% 
    mutate(rank = rank(-Count)) %>%  #Ranking the baby names, with 1 being the most popular name in that year for its respective gender
    ungroup() %>% 
    filter(rank <= 25) %>%  #Only keeping the 25 most popular names per gender per year
  mutate(Year_plus_3 = Year + 3) 


  spearman_rank_df <- spearman_rank_df %>% 
    left_join( spearman_rank_df %>%
      select(Name, Gender, Year, future_rank = rank),    #Creating a column which is the rank of that name in three years time
    by = c("Name", "Gender", "Year_plus_3" = "Year")) %>% 
    filter(!is.na(future_rank)) %>% 
    group_by(Year, Gender) %>% 
    summarise(
    corr = cor(rank, future_rank, method = "spearman", use = "complete.obs"),
    .groups = "drop")      #Creating a column which is the correlation between the rankings of the top 25 boy names and top 25 girl names in that current year and 3 years later
```

Doing the same data wrangling process, but specifically for New York
```{r}
spearman_rank_df_NY <- Baby_names %>% 
    filter(State == "NY") %>% 
    group_by(Year, Gender) %>% 
    mutate(rank = rank(-Count)) %>% 
    ungroup() %>% 
    filter(rank <= 25) 

spearman_rank_df_NY <- spearman_rank_df_NY %>% 
  mutate(Year_plus_3 = Year + 3) %>%
  left_join( spearman_rank_df_NY %>%
      select(Name, Gender, Year, future_rank = rank),
    by = c("Name", "Gender", "Year_plus_3" = "Year")) %>% 
    filter(!is.na(future_rank)) %>% 
    group_by(Year, Gender) %>% 
    summarise(
    corr = cor(rank, future_rank, method = "spearman", use = "complete.obs"),
    .groups = "drop")
```

A function which creates a line graph of a correlation coefficient over time using ggplot. It takes several labels as arguments, as well as user-defined vertical lines to create emphasis in changes between years, etc. Here, it plots the correlation between popular names in the current period and popular names in three years time. I input 1990 and 2003 as vertical lines.
```{r}
#Creating the plot for name persistence in the US across time

#The dataframe must contain a Gender column with M and F, a Year column, and a corr column
US_name_persistence_graph <- correlation_over_time_graph(data = spearman_rank_df, y_label = "Persistence of Names In The US", x_breaks = c(1910, 1925, 1950, 1975, 1990, 2003, 2011), vlines = c(1990, 2003))

##Creating the plot for name persistence in NY across time
NY_name_persistence_graph <- correlation_over_time_graph(data = spearman_rank_df_NY, x_label = "Year", y_label = "Persistence of Names In NY", x_breaks = c(1910, 1925, 1950, 1975, 1990, 2003, 2011), vlines = c(1990, 2003), linetype = "dotted", suppress_legend = T)

#Using patchwork package to stack the above two graphs on top of one another. Centering the title and putting the colour legend to the right
name_persistence_plot <- US_name_persistence_graph / NY_name_persistence_graph + plot_annotation(title = "Name Persistence", theme = theme(plot.title = element_text(hjust = 0.5))) + 
    plot_layout(guides = "collect") +
    theme(legend.position = "right")

#Saving the patchwork graph to my output folder
ggsave(filename = "name_persistence_plot.png", plot = name_persistence_plot, device = "png", path = "output/")
```

Wrangling the data to identify the top music artists of each decade
```{r}
popular_artists <- music_charts %>% 
    
    #renaming the columns to fit R naming norms
    rename(weeks_on_board = `weeks-on-board`, peak_rank = `peak-rank`) %>% 
    mutate(date = as.Date(date)) %>% 
    
    #Using my decade function to create a column which takes on the value of the decade that the date is in
    decade(., date) %>% 
    
    #Filtering for relevant dates given the baby name data
    filter(date >= lubridate::ymd(19100101) & date <= lubridate::ymd(20141231)) %>%
    
    #Removing features from artist names, and splitting up the observation if more than one main artist is credited
    mutate(artist = str_remove(artist, regex(" featuring .*", ignore_case = T))) %>%
    mutate(artist = str_remove(artist, regex( "With .*", ignore_case = T))) %>% 
    separate_rows(artist, sep = " & ") %>%
    separate_rows(artist, sep = ",") %>% 
     mutate(artist = str_trim(artist)) %>% 
    group_by(song) %>% 
    
    #Only keeping the last week which the song was on the charts, so that the "weeks_on_board" column represents the total number of weeks a song was ever on the charts for
    filter(weeks_on_board == max(weeks_on_board)) %>% 
    ungroup()  %>% 
    
    #Using my song_ranking function to calculate an overall song ranking. It divides the total number of weeks a song was on the chart by the songs peak rank(so songs which got a high ranking(lower number) and a large number of weeks on the charts will have a high overall ranking)
    song_ranking(weeks_on_board, peak_rank) %>% 
    group_by(artist, decade) %>% 
    
    #Calculating an artists overall popularity by summing together the scores of all their songs on the charts
    summarise(artist_popularity = sum(overall_song_rank)) %>% 
    group_by(decade)%>% 
    
    #Selecting the most popular artist per decade
    slice_max(order_by = artist_popularity, n = 1, with_ties = FALSE) %>%
  ungroup()
```

Creating a neat table of most popular artist per decade to put into the pdf using the stargazer package and saving it to my output folder
```{r}
popular_artists_save <- gt(popular_artists) %>% 
    gtsave(filename = "popular_artists_save.png", path = "output/", vwidth = 400, vheight = 250, expand = 1)
```

Finding the most popular movie per decade
```{r}
popular_movies <- HBO_titles %>% 
    
    #Filtering for the relevant dates based on the baby name data, and using my decade function to create a variable which states the decade in which the movie was released
    mutate(release_year = as.Date(paste0(release_year, "-01-01"))) %>% 
    filter(release_year >= lubridate::ymd(19100101) & release_year <= lubridate:: ymd(20140101)) %>% 
    decade(., release_year) %>% 
    mutate(release_year = lubridate::year(release_year)) %>% 
    
    #Selecting the most popular movie per decade
    group_by(decade) %>% 
    slice_max(order_by = tmdb_popularity, n = 1, with_ties = F) %>% 
    select(decade, tmdb_popularity, title, id) %>% 
    ungroup()
```

Wrangling the HBO_credits data in the aim of finding the actors from the most popular movie per decade
```{r}
popular_actors <- HBO_credits %>% 
    #Only keeping actors as directors usually don't become super famous
    filter(role == "ACTOR") %>% 
    select(id, name, character) %>% 
    
    #Filtering out any characters which were uncredited, as those actors wouldn't have had any popularity
    filter(!str_detect(character, "\\(uncredited\\)")) %>% 
    filter(!str_detect(character, "\\(Uncredited\\)"))
```

Finding the actors and characters from the most popular movie per decade
```{r}
#Combining the two datasets above, so that there is a list of actors and characters of each most popular movie
popular_actors <- left_join(popular_movies, popular_actors, by = "id")

#Creating a dataset of just the characters for each popular movie
popular_characters <- popular_actors %>% 
    select(-name) %>% 
    filter(!is.na(character)) %>% 
    
    #Only keeping the first names of each character
    mutate(character = word(character))

#Creating a dataset of just the actors from each popular movie
popular_actors <- popular_actors %>% 
    select(-character) %>% 
    
    #Only keeping the first name of each actor 
    mutate(name = word(name)) %>% 
    filter(!is.na(name))
```

Calculating the count of each baby name per decade
```{r}
popular_names <- Baby_names %>% 
     #Aggregating the count per names per state, so that count represents the number of babies given that name in that year in the entirety of the US. The state column is dropped by this function.
    group_by(Year, Name, Gender) %>% 
    summarise(Count = sum(Count)) %>% 
    ungroup() %>% 
    mutate(Year = as.Date(paste0(Year, "-01-01"))) %>% 
    
    #Using my decade function to create a decade column and from there calculating the most popular names per decade. I do this in a genderless manner as famous names may be given to a boy or a girl(there are observations of even John being a female name)
    decade(., Year) %>% 
    mutate(Year = lubridate::year(Year)) %>% 
    group_by(Name, decade) %>%
    summarise(Count = sum(Count)) %>% 
    
    #I log the Count variable as there is a large difference in the absoloute values for different names, which makes graphs extremely difficult to visualise
    mutate(Count = log(Count))
```

Manually selecting some famous names for analysis
```{r}
#Manually creating this vector of famous actors/characters/singers which I found in the datasets I created of the most popular type of the respective celebrity per decade(John and Paul are from the Beatles)
famous_names <- c("Charlie", "Dorothy", "John", "Paul", "Mariah", "Elvis")

#Creating a dataframe of the names which the famous people above had, and how those names' rankings changed over the decades
famous_names_over_time <- popular_names %>% 
    filter(Name %in% famous_names)
```

I attempted to create a ridgeline graph, however the counts were too big and I could not find a way to scale each individual y-axis, so they did not provide much detail. I wanted each ridgeline to represent a famous name, and it would fluctuate with the popularity of that name over the decades. This would highlight when names became most popular or increased in popularity, and could be compared with the peak fame of the relative celebrity. For measurements of name popularity, I tried using total count, scaled total count, log of total count, percentage of total names that year, and rankings of popular names, however none could get the graphs to provide nice enough detail for visual comparison
```{r}
#name_ridgeline <- famous_names_over_time %>% 
    #ggplot(aes(x = decade, y = Name, fill = Name)) +
    #stat_density_ridges(stat = "identity", scale = 0.7, real_min_height = 0.001) +
  #scale_x_continuous(breaks = c(seq(1910, 2010, 10), 2014)) +
    #scale_y_continuous(limits = c(5000, NA)) +
  #labs(
    #title = "Popularity of Famous Names Over Time",
    #x = "Decade",
    #y = "Name"
  #) +
  #theme_bw()

#name_ridgeline
```

A function which plots the Log Count of a list of names over time. It is intended to be accompanied with celebrity names, which are represented with a dot in the decade they were most famous(this information was gotten from the most popular actor/artist/character datasets that I created earlier). It takes a vector of first names matched with respective full celebrity names, and a vector of the first name of the celebrity with their respective decade of peak fame as arguments.
```{r}
famous_names_over_time_plot <- plot_famous_names_over_time(famous_names_over_time, celebrity_names = c("Charlie" = "Charlie Chaplin", "Dorothy" = "Wizard of Oz Dorothy", "Elvis" = "Elvis Presley", "John" = "John Lennon", "Paul" = "Paul McCartney", "Mariah" = "Mariah Carey"), 
label_decades = label_decades <- c( "Charlie" = 1920, "Dorothy" = 1930, "Elvis" = 1950, "John" = 1960, "Paul" = 1960, "Mariah" = 1990), start_year = 1910, end_year = 2010)

#Saving the graph to my output folder
ggsave("famous_names_over_time_plot.png", plot = famous_names_over_time_plot, device = "png", path = "output/")
```
