---
title: "README_Question_3"
author: "Matt Kruger"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Loading packages
```{r}
install.packages("pacman")
pacman::p_load("tidyverse")
pacman::p_load("lubdridate")
pacman::p_load("stringr")
pacman::p_load("ggridges")
pacman::p_load("patchwork")
pacman::p_load("stargazer")
pacman::p_load("gt")
pacman::p_load("webshot")
webshot::install_phantomjs()
pacman::p_load("webshot2")
pacman::p_load("forcats")
pacman::p_load("ggsci")
pacman::p_load("readr")
pacman::p_load("huxtable")
```

Reading in the data
```{r}
netflix <- read.csv(file = "../data/PracData25/netflix/netflix_movies.csv", header = T)
credits <- read_rds(file = "../data/PracData25/netflix/credits.rds")
titles <- read_rds(file = "../data/PracData25/netflix/titles.rds")
HBO <- read_rds(file = "../data/PracData25/US_Baby_names/HBO_titles.rds")
```

Loading in functions
```{r}
list.files('code/', full.names = T, recursive = T) %>% .[grepl('.R', .)] %>% as.list() %>% walk(~source(.))
```

Creating a dataframe which I will use to create a regression in order to see the factors which affect movie popularity
```{r}
#Creatng a vector of all the movie names which are on Netflix
netflix_movies <- netflix %>% 
    filter(type == "Movie") %>% 
    pull(title)

#Filtering the titles dataframe to only contain movies which are on Netflix
netflix_titles <- titles %>% 
    filter(title %in% netflix_movies) %>% 
    #Only slecting the variables which I need from the titles dataframe
    select(title, imdb_score, tmdb_popularity, genres)

#Creating the dataframe for the regression by joining the filtered titles datafram with the Netflix dataframe
regression_df <- left_join(netflix_titles, netflix, by = "title") %>% 
    
    #Removing the word "min" from all duration observations and turning it into a numeric variable
    mutate(duration = as.numeric(str_remove(duration, " min"))) %>% 
    
    #Filtering out a wrongly recorded rating variable
    filter(!rating == "84 min")
```

Only keeping the top 5 most popular countries where movies are produced, as these are likely to have the most significant impact on the popularity of a movie. I do this by using my top_5_x function which outputs the top 5 most popular observations for a variable.
```{r}
top_5_countries <- regression_df %>% 
    top_5_x(country)

#Filtering the regression dataframe to only contain movies made in the top 5 most popular countries
regression_df <- regression_df %>% 
    semi_join(top_5_countries, by = "country")
```

Cleaning up the genres variable by firstly ensuring that each observation has only one genre assigned to it. Many of the same genres had two types of observation, one with a leading space and one without.I used my remove_leading_space function to ensure all observations for one genre were the same. I then also selected the top 5 most common genres and filtered the regression dataframe to only contain these, as they are likely to have the most significant effect on the popularity of a movie. 
```{r}
regression_df <- regression_df %>% 
    #Ensuring that all genre observations were represented by one clean word
     mutate(genres = str_remove_all(genres, "\\[|\\]|'|\"")) %>% 
    separate_rows(genres, sep = ",") %>% 
    
    #Unifying all typos, so that each genre had one observation type
    remove_leading_space(genres, "drama") %>% 
    remove_leading_space(genres, "comedy") %>% 
    remove_leading_space(genres, "action") %>% 
    remove_leading_space(genres, "romance") %>% 
    remove_leading_space(genres, "crime")

#Identifying top 5 genres
top_5_genres <- regression_df %>% 
    top_5_x(genres)

#Filtering the regression dataframe to contain only the movies in the top 5 genres
regression_df <-regression_df %>% 
    semi_join(top_5_genres, by = "genres")
```

Obtaining the top 5 most common ratings and filtering the regression dataframe to only contain movies with these ratings, as they are likely to have the most significant effect on the popularity of a movie.
```{r}
top_5_ratings <- regression_df %>% 
    top_5_x(rating)

regression_df <- regression_df %>% 
    semi_join(top_5_ratings, by = "rating")
```

Using my factor_transformation function to ensure all categorical variables are factors, and manually set the reference category. This makes the following regression more interpretable and customizable.
```{r}
regression_df <- regression_df %>% 
     factor_transformation(country, "United States") %>% 
    factor_transformation(genres, "drama") %>% 
    factor_transformation(rating, "TV-MA")
```

Creating the regression. I analyse the effects of country, genre, movie length, imdb score, the year of release(in order to control for time effects), and rating
```{r}
movie_regression <- regression_df %>% 
    lm(formula = tmdb_popularity ~ country + genres + duration + imdb_score + release_year + rating)
```

Creating a regression table using the huxtable package 
```{r}
regression_table <- huxreg(
  "Popularity" = movie_regression,         
  number_format = "%.2f",   #Rounds all values to two decimal places                
  align = ".",   #aligns values by decimal point                           
  omit_coefs = "release_year",             
  stars = c(`***` = 0.001, `**` = 0.01, `*` = 0.05)
)

quick_html(regression_table, file = "regtable.html")
webshot("regtable.html", file = "output/regtable.png")
```
 
Creating a dataframe for the ridgeline plot 
```{r}
ridgeline_df <- regression_df %>% 
    #Anlysing more recent movies for relevance
    filter(release_year >= 2010) %>% 
    
    #Only a few outliers outside of this range which made the graph uninterpretable
    filter(tmdb_popularity <= 30)
```

Creating the ridgeline plot of the distribution of popularity scores for different gernes of movies using my ridgeline function
```{r}
genre_ridgeline <- ridgeline(ridgeline_df, x_axis = tmdb_popularity, y_axis = genres, x_lab = "Popularity", y_lab = "Genres", title = "Distribution of Scores Per Genre")

#saving my ridgeline plot to my output folder
ggsave(filename = "ridgeline.png", path = "output/", plot = genre_ridgeline, device = "png")
```






